--- 
title: "Bombus haemolymph diapause study"
output: bombus_queen_haemolymph_stats.html
authors: Joe Colgan (joscolgan)
--- 

## Introduction:
The purpose of this script is to take label-free quantification (LFQ) values from the software program, [Perseus](https://www.biochem.mpg.de/5111810/perseus) and perform:
1) A One-way ANOVA to identify differentially abundant proteins across six bumblebee queen life-stages;
2) Pairwise t-tests comparisons between each life-stages;
3) Subset pairwise comparisons between consecutive life-stages.
This script outputs tab-delimited text files containing results of ANOVA and pairwise t-tests.

```{r, message = FALSE}
# Load libraries; install from scratch if needed
libraries <- c("lintr",
               "dplyr")
for (lib in libraries) {
    if (require(package = lib, character.only = TRUE)) {
        print("Successful")
    } else {
        print("Installing")
        source("https://bioconductor.org/biocLite.R")
        biocLite(pkgs = lib)
        library(lib, character.only = TRUE )
    }
}
dir.create("results")
```

Read in input data:

```{r}
## Read in data and store as a dataframe:
haem_data <- read.table(file = "input/diapause_results_111118_for_pca.txt",
                        header = TRUE)

## Assign the first column containing protein_id to the rowname:
rownames(haem_data) <- haem_data$T._Protein_ID

## Remove the protein ID column:
haem_data$T._Protein_ID <- NULL
haem_data$T._Fasta_headers <- NULL

## Transpose:
haem_data_df <- as.data.frame(t(haem_data))

## Add a column indicating life cycle 'stage':
rownames(haem_data_df)

## Update stage:
life_stages <- c(rep("gyne", 4),
                 rep("prediapause", 4),
                 rep("early_diapause", 4),
                 rep("late_diapause", 4),
                 rep("six_hours_postdiapause", 4),
                 rep("forty_eight_hours_postdiapause", 4))

## Add column for life cycle stage:
haem_data_df$life_stages <- life_stages

## Add levels for plotting:
haem_data_df$life_stages <- factor(haem_data_df$life_stages,
                             levels = c(unique(as.character(unlist(haem_data_df$life_stages)))))

## Perform ANOVA:
levels(haem_data_df$life_stages)

## Perform a one_way ANOVA: 
anova_df <- data.frame(matrix(ncol = 10,
                              nrow = 0),
                       stringsAsFactors = FALSE)

colnames(anova_df) <- c("DF1",
                      "DF2",
                      "sum_sq1",
                      "sum_sq2",
                      "mean_sq1",
                      "mean_sq2",
                      "f_value1",
                      "f_value2",
                      "P_value",
                      "sig")
tukey_output <- data.frame()
tukey_output_df_sig <- data.frame()
for (protein in 1:(ncol(haem_data_df) - 1)){
        res_aov <- aov(haem_data_df[, protein] ~ life_stages,
                       data = haem_data_df)
        anova_df[nrow(anova_df) + 1, ] <- as.numeric(unlist(summary(res_aov)))
        tukey_output <- TukeyHSD(res_aov)
        tukey_output_df <- as.data.frame(tukey_output$life_stages)
        ## Update rowname:
        rownames(tukey_output_df) <- paste(rownames(tukey_output_df),
                 "-",
                 colnames(haem_data_df)[protein],
                 sep = "")
        colnames(tukey_output_df) <- c("diff",
                                       "lwr",
                                       "upr",
                                       "p_adj")
        tukey_output_df$protein <- colnames(haem_data_df)[protein]
        tukey_output_df_sig <- rbind(tukey_output_df_sig,
                                     subset(tukey_output_df,
                                            p_adj < 0.05))
}

## Add protein IDs:
anova_df$protein_id <- rownames(haem_data)

## Write to file:
write.table(anova_df,
            file = "./results/anova_output.txt",
            quote = FALSE,
            sep = "\t",
            row.names = FALSE)

write.table(tukey_output_df_sig,
            file = "./results/tukey_output.txt",
            quote = FALSE,
            sep = "\t",
            row.names = TRUE)
```

Performing a two-sample t-test:

```{r, message = FALSE}
## Perform two_sample t_tests between consecutive stages:
p_values_df <- data.frame()
for (protein in 1:(ncol(haem_data_df) - 1)){
        comparisons <- pairwise.t.test(haem_data_df[[protein]],
                haem_data_df$life_stages,
                 p.adjust.method = "BH")
        comparisons_df <- as.data.frame(comparisons$p.value)
        comparisons_df$protein <- colnames(haem_data_df)[protein]
        p_values_df <- rbind(comparisons_df,
                             p_values_df)
}

## Update columns for subsetting significant proteins from consecutive pairwise comparisons:
colnames(p_values_df) <- c("gyne",
                           "prediapause",
                           "early_diapause",
                           "late_diapause",
                           "six_hours_postdiapause",
                           "forty_eight_hours_postdiapause")

## Create directory for output:
dir.create(path = "./results/dataframes",
           recursive = TRUE)

for (name in 1:(length(colnames(p_values_df[1:5])))){
        new_stage <- name + 1
        print(colnames(p_values_df[name]))
        stage_of_interest <- colnames(p_values_df[new_stage])
        print(stage_of_interest)
        output_df <- subset(p_values_df,
                            p_values_df[name] < 0.05 &
                                    grepl(paste("^",
                                                stage_of_interest,
                                   sep = ""),
                             row.names(p_values_df)))
        ## Write output:
        output <- paste(colnames(p_values_df[name]),
                                 "_vs_",
                                 colnames(p_values_df[new_stage]),
                        ".txt",
                        sep = "")
        ## Write to file:
        write.table(output_df,
                    file = paste("./results/dataframes/",
                                 output,
                                 sep = ""),
                    sep = "\t",
                    quote = FALSE)
}
```
Check style:

```{r, message = FALSE}
## Run lintr:
lintr::lint(file = "./bombus_queen_haemolymph_stats.Rmd")
```


