--- 
title: "Bombus haemolymph diapause study"
output: gene_level_differential_expression_diapause.html
authors: Joe Colgan (joscolgan)
--- 

Introduction:
The purpose of this script is to take label-free quantification (LFQ) values from the software program, Perseus, normalise and perform a principal component analysis. Two principal components are then plotted using the R package, ggplot2. 

```{r}
# Load libraries; install from scratch if needed
libraries <- c("ggplot2", "ggfortify", "RColorBrewer", "ggpubr")
for (lib in libraries) {
    if (require(package = lib, character.only = TRUE)) {
        print("Successful")
    } else {
        print("Installing")
        source("https://bioconductor.org/biocLite.R")
        biocLite(pkgs = lib)
        library(lib, character.only = TRUE )
    }
}
dir.create("results")
```

1. Read in input data:

```{r}
## Read in data and store as a dataframe:
haem_data <- read.table(file = "input/diapause_results_061118_for_pca_updated_names.txt", header = TRUE)

## Assign the first column containing protein_id to the rowname:
rownames(haem_data) <- haem_data$T._Protein_ID

## Remove the protein ID column:
haem_data$T._Protein_ID <- NULL

## Transpose:
haem_data_df <- as.data.frame(t(haem_data))

## Add a column indicating life-cycle 'stage':
rownames(haem_data_df)

## Update stage:
stage <- c(rep("gyne", 4), rep("prediapause", 4), rep("early_diapause", 4),
           rep("late_diapause", 4), rep("6_hrs_postdiapause", 4), rep("48_hours_postdiapause", 4))

## Add column for life cycle stage:
haem_data_df$stage <- stage 

## Add levels for plotting:
haem_data_df$stage <- factor(haem_data_df$stage,
                             levels = c(unique(as.character(unlist(haem_data_df$stage)))))

## Subset for plotting:
haem_data_subset <- haem_data_df[,c(1:70)]
```

2. Perform PCA and plot:

```{r}
## Perform PCA:
haem_data_subset_pca <- prcomp(haem_data_subset,
                 center = TRUE,
                 scale. = TRUE) 

## Plot all principal components:
plot(haem_data_subset_pca, type = "l")

## Perform PCA and plot first two components:
pca_plot <- autoplot(prcomp(haem_data_subset), x=1, y=5,
                #scale. = TRUE,
                #center = TRUE), 
         data=haem_data_df, 
         colour = "stage",
         fill = "black",
         size = 4) +
         #label = TRUE) +
        scale_color_brewer(type="qual", palette="RdBu") +
        geom_point(aes(colour=haem_data_df$stage), size = 6) + 
        geom_point(shape = 1,size = 6,colour = "black") +
        theme_bw()

## Increase the font size:
pca_plot<- pca_plot +
                theme(axis.text=element_text(size=15),
                axis.title= element_text(size=15,face="bold"))
                #axis.text.x=element_text(size=12),
                #axis.text.y = element_text(size=12))
```

Plot a number of principal components:

```{r}
## Plot
pca_plot_1_2 <- autoplot(prcomp(haem_data_subset), x=1, y=2,
                #scale. = TRUE,
                #center = TRUE), 
         data=haem_data_df, 
         colour = "stage",
         fill = "black",
         size = 4) +
         #label = TRUE) +
        scale_color_brewer(type="qual", palette="RdBu") +
        geom_point(aes(colour=haem_data_df$stage), size = 6) + 
        geom_point(shape = 1,size = 6,colour = "black") +
        theme_bw() +
        theme(axis.text=element_text(size=15),
                axis.title= element_text(size=15,face="bold"))

## Plot principal components 1 and 3:
pca_plot_1_3 <- autoplot(prcomp(haem_data_subset), x=1, y=3,
                #scale. = TRUE,
                #center = TRUE), 
         data=haem_data_df, 
         colour = "stage",
         fill = "black",
         size = 4) +
         #label = TRUE) +
        scale_color_brewer(type="qual", palette="RdBu") +
        geom_point(aes(colour=haem_data_df$stage), size = 6) + 
        geom_point(shape = 1,size = 6,colour = "black") +
        theme_bw() +
        theme(axis.text=element_text(size=15),
                axis.title= element_text(size=15,face="bold"))

## Plot principal components 1 and 4:
pca_plot_1_4 <- autoplot(prcomp(haem_data_subset), x=1, y=4,
                #scale. = TRUE,
                #center = TRUE), 
         data=haem_data_df, 
         colour = "stage",
         fill = "black",
         size = 4) +
         #label = TRUE) +
        scale_color_brewer(type="qual", palette="RdBu") +
        geom_point(aes(colour=haem_data_df$stage), size = 6) + 
        geom_point(shape = 1,size = 6,colour = "black") +
        theme_bw() +
        theme(axis.text=element_text(size=15),
                axis.title= element_text(size=15,face="bold"))

## Plot principal components 1 and 5:
pca_plot_1_5 <- autoplot(prcomp(haem_data_subset), x=1, y=5,
                #scale. = TRUE,
                #center = TRUE), 
         data=haem_data_df, 
         colour = "stage",
         fill = "black",
         size = 4) +
         #label = TRUE) +
        scale_color_brewer(type="qual", palette="RdBu") +
        geom_point(aes(colour=haem_data_df$stage), size = 6) + 
        geom_point(shape = 1,size = 6,colour = "black") +
        theme_bw() +
        theme(axis.text=element_text(size=15),
                axis.title= element_text(size=15,face="bold"))
```

Plot together:

```{r}
## Plot together:
ggarrange(pca_plot_1_2,
          pca_plot_1_3,
          pca_plot_1_4,
          pca_plot_1_5,
          labels = c("A", "B", "C", "D"),
          nrow = 2, ncol =2,
          common.legend = TRUE)

## Save as a .png file:
ggsave(file="results/pca_1_5_haemolymph_life_cycles_RdBu.png",
       height = 10,
       width = 10)

```

Look at additional components:

```{r}
## Plot
pca_plot_2_3 <- autoplot(prcomp(haem_data_subset), x=2, y=3,
                #scale. = TRUE,
                #center = TRUE), 
         data=haem_data_df, 
         colour = "stage",
         fill = "black",
         size = 4) +
         #label = TRUE) +
        scale_color_brewer(type="qual", palette="RdBu") +
        geom_point(aes(colour=haem_data_df$stage), size = 6) + 
        geom_point(shape = 1,size = 6,colour = "black") +
        theme_bw() +
        theme(axis.text=element_text(size=15),
                axis.title= element_text(size=15,face="bold"))

## Plot principal components 3 and 4:
pca_plot_3_4 <- autoplot(prcomp(haem_data_subset), x=3, y=4,
                #scale. = TRUE,
                #center = TRUE), 
         data=haem_data_df, 
         colour = "stage",
         fill = "black",
         size = 4) +
         #label = TRUE) +
        scale_color_brewer(type="qual", palette="RdBu") +
        geom_point(aes(colour=haem_data_df$stage), size = 6) + 
        geom_point(shape = 1,size = 6,colour = "black") +
        theme_bw() +
        theme(axis.text=element_text(size=15),
                axis.title= element_text(size=15,face="bold"))

## Plot principal components 4 and 5:
pca_plot_4_5 <- autoplot(prcomp(haem_data_subset), x=4, y=5,
                #scale. = TRUE,
                #center = TRUE), 
         data=haem_data_df, 
         colour = "stage",
         fill = "black",
         size = 4) +
         #label = TRUE) +
        scale_color_brewer(type="qual", palette="RdBu") +
        geom_point(aes(colour=haem_data_df$stage), size = 6) + 
        geom_point(shape = 1,size = 6,colour = "black") +
        theme_bw() +
        theme(axis.text=element_text(size=15),
                axis.title= element_text(size=15,face="bold"))

## Plot principal components 1 and 5:
pca_plot_5_6 <- autoplot(prcomp(haem_data_subset), x=5, y=6,
                #scale. = TRUE,
                #center = TRUE), 
         data=haem_data_df, 
         colour = "stage",
         fill = "black",
         size = 4) +
         #label = TRUE) +
        scale_color_brewer(type="qual", palette="RdBu") +
        geom_point(aes(colour=haem_data_df$stage), size = 6) + 
        geom_point(shape = 1,size = 6,colour = "black") +
        theme_bw() +
        theme(axis.text=element_text(size=15),
                axis.title= element_text(size=15,face="bold"))

## Plot together:
ggarrange(pca_plot_2_3,
          pca_plot_3_4,
          pca_plot_4_5,
          pca_plot_5_6,
          labels = c("A", "B", "C", "D"),
          nrow = 2, ncol =2,
          common.legend = TRUE)

ggsave(file="pca_2_6_combo_haemolymph_life_cycles.png",
       height = 10,
       width = 10)


```

Look at movement of individual proteins:

```{r}
## Perform PCA:
haem_data_pca <- prcomp(haem_data,
                 center = TRUE,
                 scale. = TRUE) 

## Plot all principal components:
plot(haem_data_pca, type = "l")

## Perform PCA and plot first two components:
pca_plot <- autoplot(prcomp(haem_data), x=1, y=3,
                #scale. = TRUE,
                #center = TRUE), 
         data=haem_data, 
         #colour = "stage",
         #fill = "black",
         size = 2, 
         label = FALSE) +
        #scale_color_brewer(type="qual", palette="RdBu") +
        geom_point(size = 1) + 
        #geom_point(shape = 1,size = 6,colour = "black") +
        theme_bw()

## Increase the font size:
pca_plot<- pca_plot +
                theme(axis.text=element_text(size=15),
                axis.title= element_text(size=15,face="bold"))

pca_plot


ggplot(data = haem_data_pca, aes(x = PC1, y = PC2))+
        geom_point()

## Sort by first principal componenet:
sort(haem_data_pca$x[,1])


```



