--- 
title: "Bombus haemolymph diapause study"
output: bombus_queen_haemolymph_proteome_hahp_boxplots.html
authors: Joe Colgan (joscolgan)
--- 

## Introduction:

The purpose of this script is to take label-free quantification (LFQ) values from the software program, [Perseus](https://www.biochem.mpg.de/5111810/perseus), z-score normalise and plot as boxplots using the R package, [ggplot2](https://ggplot2.tidyverse.org/).  
This script outputs an image saved as either .png, .jpeg or .pdf.

The first step involves loading required libraries:

```{r, message = FALSE}
# Load libraries; install from scratch if needed
libraries <- c("ggplot2",
               "ggfortify",
               "RColorBrewer",
               "ggpubr",
               "reshape",
               "matrixStats",
               "ggsignif")
for (lib in libraries) {
    if (require(package = lib, character.only = TRUE)) {
        print("Successful")
    } else {
        print("Installing")
        source("https://bioconductor.org/biocLite.R")
        biocLite(pkgs = lib)
        library(lib, character.only = TRUE )
    }
}

## Script will comlain if already exists:
dir.create("results")
```

Read in input data:

```{r, message = FALSE}
## Read in data and store as a dataframe:
haem_data <- read.table(file = "input/input_for_plots.txt",
                        header = TRUE)

## Assign the first column containing protein_id to the rowname:
rownames(haem_data) <- haem_data$T._Protein_ID

## Subset columns containing intensity values:
haem_data_subset <- haem_data[, 3:26]
head(haem_data_subset)

## Transpose:
haem_data_df <- as.data.frame(t(haem_data_subset))

## Add a column indicating life cycle 'stage':
rownames(haem_data_df)
```

Subset proteins of interest and plot:

```{r, message = FALSE}
## Update column names:
## The dataframe needs to be rearranged for boxplots:
## Subset based on a list of proteins:
proteins_of_interest <- read.table(file = "data/hahp_family.txt",
                              header = FALSE)

## Update column names:
colnames(proteins_of_interest) <- c("description", "protein_id")

## Remove species ID:
proteins_of_interest$description <- gsub("Bombus_terrestris",
                                         "",
                                         proteins_of_interest$description)
proteins_of_interest$description <- gsub("\\[]",
                                         "",
                                         proteins_of_interest$description)
proteins_of_interest$description <- gsub("_",
                                         " ",
                                         proteins_of_interest$description)
## Subset proteins of interest:
tmp <- subset(haem_data_subset, row.names(haem_data_subset)
              %in% proteins_of_interest$protein_id)

## Transpose:
tmp_trans <- t(tmp)

## For each proteins reformat:
reformat_for_plot <- function(input,
                              protein,
                              description,
                              compare_1,
                              compare_2,
                              compare_3,
                              compare_4){
        print(protein)
        protein_tmp <- input[, protein]
        gyne <- protein_tmp[1:4]
        prediapause <- protein_tmp[5:8]
        early_diapause <- protein_tmp[9:12]
        late_diapause <- protein_tmp[13:16]
        early_postdiapause <- protein_tmp[17:20]
        late_postdiapause <- protein_tmp[21:24]
        ## Recombine
        protein_df <- cbind(gyne,
                            prediapause,
                            early_diapause,
                            late_diapause,
                            early_postdiapause,
                            late_postdiapause)
        ## Rename columns:
        colnames(protein_df) <- c("gyne",
                                  "pre-diapause",
                                  "early diapause",
                                  "late diapause",
                                  "6 hrs postdiapause",
                                  "48 hrs postdiapause")
        ## Make sure it is a dataframe:
        protein_df <- as.data.frame(protein_df)
        ## Reshape for plotting:
        protein_df_melt <- melt(protein_df)
        ## Update column names:
        colnames(protein_df_melt) <- c("Life_stage",
                                       "Log2_values")
        ## Plot:
        protein_plot <- ggplot(protein_df_melt,
                               aes(x = Life_stage,
                                   y = Log2_values,
                                   fill = Life_stage)) +
                geom_boxplot() +
                xlab("Life stage") +
                ylab("LFQ Intensities") +
                theme(legend.position = "none") +
                ggtitle(description) +
                scale_fill_brewer(name = "Life stages",
                                  type = "qual",
                                  palette = "RdBu") +
                theme_bw() +
                theme(legend.position = "top")
        protein_plot <- protein_plot +
                theme(axis.text = element_text(size = 10),
                      axis.title = element_text(size = 10,
                                                face = "bold"),
                      axis.text.x = element_blank(),
                      plot.title = element_text(size = 8),
                      legend.title = element_text(size = 10,
                                                 face = "bold"))
        ## Add significance values:
        protein_plot <- protein_plot +
                geom_signif(comparisons = list(c(compare_1,
                                                 compare_2)),
                            annotation = c("***"))
        protein_plot <- protein_plot +
                geom_signif(comparisons = list(c(compare_3,
                                                 compare_4)),
                            annotation = c("***"))
        ## Return plot:
        print(protein_plot)
}

length(proteins_of_interest$protein_id)

## Print all proteins of interest together:
ggarrange(reformat_for_plot(tmp_trans,
                            proteins_of_interest$protein_id[1],
                            proteins_of_interest$description[1],
                            "pre-diapause",
                            "early diapause",
                            "6 hrs postdiapause",
                            "48 hrs postdiapause"),
          nrow = 1,
          ncol = 1,
          common.legend = TRUE)

## Create directory for PDF:
dir.create(path = "./results/pdf/",
           recursive = TRUE)

## Define output:
output_pdf <- "results/pdf/hahp_box_plots.pdf"

## Save output:
ggsave(output_pdf,
       dpi = 600,
       height = 5,
       width = 5)

## Output a .png image:
dir.create(path = "./results/png/",
           recursive = TRUE)

## Define output:
output_png <- "results/png/hahp_box_plots.png"

## Save output:
ggsave(output_png,
       dpi = 600,
       height = 5,
       width = 5)
```

Run lintr:

```{r, message = FALSE}
## Run lintr:
lintr::lint(file = "./bombus_queen_haemolymph_proteome_hahp_boxplots.Rmd")
```
